EnVision CF Analyses

### 2025-09-15 Christine Chan/EnVision CF/envision_analyses.qmd
EnVision ROC updates for Christine

```{r setup}
#| include: false
library(Hmisc)
library(tidyverse)
library(arsenal)
library(pROC)
library(gt)
library(patchwork)
library(lmerTest)
library(emmeans)
home_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/tim/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF",
  "Windows" = "C:/Users/Tim/OneDrive - The University of Colorado Denver/Vigers/CF",
  "Linux" = "/home/tim/OneDrive/Vigers/CF"
)
github_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/tim/Documents/GitHub",
  "Windows" = "C:/Users/Tim/Documents/GitHub",
  "Linux" = "/home/tim/Documents/GitHub"
)
knitr::opts_knit$set(root.dir = home_dir)
```

```{r data cleaning}
# Set seed for bootstrap
set.seed(1017)
# Import data
# See GitHub/CF/Christine Chan/EnVision CF/clean_envision_data.R
load("/Users/tim/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Christine Chan/EnVision CF/Data_Clean/envision_analysis_dataset.RData")
```

@@

```{r}
# Limit to those with CGM data (based on mean glucose) and OGTT diagnosis
df <- final_df %>% filter(!is.na(mean_sensor), !is.na(Diagnosis))
# Convert CV units to match Scully et al.
df$cv <- df$cv * 100
# First CGM and OGTT pair only
df <- df %>%
  group_by(study_id) %>%
  slice_min(Date)
```

@@

@@

```{r}
r <- roc(CFRD ~ mean_sensor, data = df, quiet = T)
plot(r, print.auc = T, print.thres = T, legacy.axes = T)
ci.auc(r)
# gt(data.frame(ci.coords(r, "best",
#   best.policy = "random",
#   ret = c(c("sensitivity", "specificity", "fp", "tp", "fn", "tn"))
# ))) %>% fmt_number(decimals = 3)
gt(coords(r, "best", ret = "all")) %>% fmt_number(decimals = 3)
```

@@

```{r}
r <- roc(CFRD ~ percent_time_over_140, data = df, quiet = T)
plot(r, print.auc = T, print.thres = T, legacy.axes = T)
ci.auc(r)
# gt(data.frame(ci.coords(r, "best",
#   best.policy = "random",
#   ret = c(c("sensitivity", "specificity", "fp", "tp", "fn", "tn"))
# ))) %>% fmt_number(decimals = 3)
gt(coords(r, "best", ret = "all")) %>% fmt_number(decimals = 3)
```

@@

```{r}
r <- roc(CFRD ~ percent_time_over_180, data = df, quiet = T)
plot(r, print.auc = T, print.thres = T, legacy.axes = T)
ci.auc(r)
# gt(data.frame(ci.coords(r, "best",
#   best.policy = "random",
#   ret = c(c("sensitivity", "specificity", "fp", "tp", "fn", "tn"))
# ))) %>% fmt_number(decimals = 3)
gt(coords(r, "best", ret = "all")) %>% fmt_number(decimals = 3)
```

@@

```{r}
r <- roc(CFRD ~ gmi, data = df, quiet = T)
plot(r, print.auc = T, print.thres = T, legacy.axes = T)
ci.auc(r)
# gt(data.frame(ci.coords(r, "best",
#   best.policy = "random",
#   ret = c(c("sensitivity", "specificity", "fp", "tp", "fn", "tn"))
# ))) %>% fmt_number(decimals = 3)
gt(coords(r, "best", ret = "all")) %>% fmt_number(decimals = 3)
```

@@

```{r}
r <- roc(CFRD ~ standard_deviation, data = df, quiet = T)
plot(r, print.auc = T, print.thres = T, legacy.axes = T)
ci.auc(r)
# gt(data.frame(ci.coords(r, "best",
#   best.policy = "random",
#   ret = c(c("sensitivity", "specificity", "fp", "tp", "fn", "tn"))
# ))) %>% fmt_number(decimals = 3)
gt(coords(r, "best", ret = "all")) %>% fmt_number(decimals = 3)
```

@@

```{r}
r <- roc(CFRD ~ cv, data = df, quiet = T)
plot(r, print.auc = T, print.thres = T, legacy.axes = T)
ci.auc(r)
# gt(data.frame(ci.coords(r, "best",
#   best.policy = "random",
#   ret = c(c("sensitivity", "specificity", "fp", "tp", "fn", "tn"))
# ))) %>% fmt_number(decimals = 3)
gt(coords(r, "best", ret = "all")) %>% fmt_number(decimals = 3)
```

@@

```{r}
r <- roc(CFRD ~ a1c_result, data = df, quiet = T)
plot(r, print.auc = T, print.thres = T, legacy.axes = T)
ci.auc(r)
# gt(data.frame(ci.coords(r, "best",
#   best.policy = "random",
#   ret = c(c("sensitivity", "specificity", "fp", "tp", "fn", "tn"))
# ))) %>% fmt_number(decimals = 3)
gt(coords(r, "best", ret = "all")) %>% fmt_number(decimals = 3)
```

@@

```{r}
#| message: false
#| warning: false
#| fig-height: 12
#| fig-width: 16
# Dotplot
box_p1 <- ggplot(
  df,
  aes(x = Dysglycemia, y = percent_time_over_140, colour = Dysglycemia)
) +
  geom_jitter() +
  geom_hline(yintercept = 17.5, color = "red") +
  geom_hline(yintercept = 11.3, color = "purple") +
  ggtitle("% Time Over 140 (mg/dL)") +
  theme_bw(base_size = 12) +
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title.x = element_blank(), axis.title.y = element_blank()
  ) +
  scale_color_manual(values = c("#4DA8DA", "#80D8C3", "#FFD66B"))
box_p2 <- ggplot(
  df,
  aes(x = Dysglycemia, y = percent_time_over_180, colour = Dysglycemia)
) +
  geom_jitter() +
  geom_hline(yintercept = 3.4, color = "red") +
  geom_hline(yintercept = 3.1, color = "purple") +
  ggtitle("% Time Over 180 (mg/dL)") +
  theme_bw(base_size = 12) +
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title.x = element_blank(), axis.title.y = element_blank()
  ) +
  scale_color_manual(values = c("#4DA8DA", "#80D8C3", "#FFD66B"))
box_p3 <- ggplot(
  df,
  aes(x = Dysglycemia, y = mean_sensor, colour = Dysglycemia)
) +
  geom_jitter() +
  geom_hline(yintercept = 112, color = "red") +
  geom_hline(yintercept = 101, color = "purple") +
  ggtitle("Mean glucose (mg/dL)") +
  theme_bw(base_size = 12) +
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title.x = element_blank(), axis.title.y = element_blank()
  ) +
  scale_color_manual(values = c("#4DA8DA", "#80D8C3", "#FFD66B"))
box_p4 <- ggplot(
  df,
  aes(x = Dysglycemia, y = cv, colour = Dysglycemia)
) +
  geom_jitter() +
  geom_hline(yintercept = 30.6, color = "red") +
  geom_hline(yintercept = 27.7, color = "purple") +
  ggtitle("Coefficient of Variation (%)") +
  theme_bw(base_size = 12) +
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title.x = element_blank(), axis.title.y = element_blank()
  ) +
  scale_color_manual(values = c("#4DA8DA", "#80D8C3", "#FFD66B"))
box_p5 <- ggplot(
  df,
  aes(x = Dysglycemia, y = a1c_result, colour = Dysglycemia)
) +
  geom_jitter() +
  geom_hline(yintercept = 5.8, color = "red") +
  geom_hline(yintercept = 5.75, color = "purple") +
  ggtitle("HbA1c (%)") +
  theme_bw(base_size = 12) +
  theme(
    legend.title = element_blank(),
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title.x = element_blank(), axis.title.y = element_blank()
  ) +
  scale_color_manual(values = c("#4DA8DA", "#80D8C3", "#FFD66B"))
box_p <- box_p1 + box_p2 + box_p4 + box_p3 + box_p5 + plot_layout(ncol = 5)
box_p
```

@@

```{r}
# Fit
mod <- lmer(Glucose ~ Timepoint * Hypo70 + (1 | study_id / ogtt_num),
  data = glmm_df
)
# EM means
means <- data.frame(emmeans(mod, c("Timepoint", "Hypo70"),
  type = "response",
  pbkrtest.limit = 1e6
))
colnames(means) <- c(
  "Timepoint", "Hypo70", "Mean", "SE", "df", "CI Lower Limit", "CI Upper Limit"
)
# Plot
ggplot(means, aes(
  x = as.numeric(as.character(Timepoint)), y = Mean, colour = Hypo70,
  group = Hypo70
)) +
  geom_point() +
  geom_errorbar(aes(ymin = `CI Lower Limit`, ymax = `CI Upper Limit`),
    width = 3
  ) +
  geom_line() +
  scale_x_continuous(breaks = timepoints) +
  scale_color_manual(values = c("#66C2A5", "#FC8D62")) +
  ylab("EM Mean Glucose") +
  xlab("Timepoint") +
  theme_bw(base_size = 14) +
  theme(legend.title = element_blank())
```

@@

```{r}
# Fit
mod <- lmer(Glucose ~ Timepoint * Hypo60 + (1 | study_id / ogtt_num),
  data = glmm_df
)
# EM means
means <- data.frame(emmeans(mod, c("Timepoint", "Hypo60"),
  type = "response",
  pbkrtest.limit = 1e6
))
colnames(means) <- c(
  "Timepoint", "Hypo60", "Mean", "SE", "df", "CI Lower Limit", "CI Upper Limit"
)
# Plot
ggplot(means, aes(
  x = as.numeric(as.character(Timepoint)), y = Mean, colour = Hypo60,
  group = Hypo60
)) +
  geom_point() +
  geom_errorbar(aes(ymin = `CI Lower Limit`, ymax = `CI Upper Limit`),
    width = 3
  ) +
  geom_line() +
  scale_x_continuous(breaks = timepoints) +
  scale_color_manual(values = c("#66C2A5", "#FC8D62")) +
  ylab("EM Mean Glucose") +
  xlab("Timepoint") +
  theme_bw(base_size = 14) +
  theme(legend.title = element_blank())
```

@@

```{r}
# Fit
mod <- lmer(log(Insulin) ~ Timepoint * Hypo70 + (1 | study_id / ogtt_num),
  data = glmm_df
)
# EM means
means <- data.frame(emmeans(mod, c("Timepoint", "Hypo70"),
  type = "response",
  pbkrtest.limit = 1e6
))
colnames(means) <- c(
  "Timepoint", "Hypo70", "Mean", "SE", "df", "CI Lower Limit", "CI Upper Limit"
)
# Plot
ggplot(means, aes(
  x = as.numeric(as.character(Timepoint)), y = Mean, colour = Hypo70,
  group = Hypo70
)) +
  geom_point() +
  geom_errorbar(aes(ymin = `CI Lower Limit`, ymax = `CI Upper Limit`),
    width = 3
  ) +
  geom_line() +
  scale_x_continuous(breaks = timepoints) +
  scale_color_manual(values = c("#66C2A5", "#FC8D62")) +
  ylab("EM Mean Insulin") +
  xlab("Timepoint") +
  theme_bw(base_size = 14) +
  theme(legend.title = element_blank())
```

@@

```{r}
# Fit
mod <- lmer(log(Insulin) ~ Timepoint * Hypo60 + (1 | study_id / ogtt_num),
  data = glmm_df
)
# EM means
means <- data.frame(emmeans(mod, c("Timepoint", "Hypo60"),
  type = "response",
  pbkrtest.limit = 1e6
))
colnames(means) <- c(
  "Timepoint", "Hypo60", "Mean", "SE", "df", "CI Lower Limit", "CI Upper Limit"
)
# Plot
ggplot(means, aes(
  x = as.numeric(as.character(Timepoint)), y = Mean, colour = Hypo60,
  group = Hypo60
)) +
  geom_point() +
  geom_errorbar(aes(ymin = `CI Lower Limit`, ymax = `CI Upper Limit`),
    width = 3
  ) +
  geom_line() +
  scale_x_continuous(breaks = timepoints) +
  scale_color_manual(values = c("#66C2A5", "#FC8D62")) +
  ylab("EM Mean Insulin") +
  xlab("Timepoint") +
  theme_bw(base_size = 14) +
  theme(legend.title = element_blank())
```

@@

```{r}
# Fit
mod <- lmer(log(C.Peptide) ~ Timepoint * Hypo70 + (1 | study_id / ogtt_num),
  data = glmm_df
)
# EM means
means <- data.frame(emmeans(mod, c("Timepoint", "Hypo70"),
  type = "response",
  pbkrtest.limit = 1e6
))
colnames(means) <- c(
  "Timepoint", "Hypo70", "Mean", "SE", "df", "CI Lower Limit", "CI Upper Limit"
)
# Plot
ggplot(means, aes(
  x = as.numeric(as.character(Timepoint)), y = Mean, colour = Hypo70,
  group = Hypo70
)) +
  geom_point() +
  geom_errorbar(aes(ymin = `CI Lower Limit`, ymax = `CI Upper Limit`),
    width = 3
  ) +
  geom_line() +
  scale_x_continuous(breaks = timepoints) +
  scale_color_manual(values = c("#66C2A5", "#FC8D62")) +
  ylab("EM Mean C-peptide") +
  xlab("Timepoint") +
  theme_bw(base_size = 14) +
  theme(legend.title = element_blank())
```

@@

```{r}
# Fit
mod <- lmer(log(C.Peptide) ~ Timepoint * Hypo60 + (1 | study_id / ogtt_num),
  data = glmm_df
)
# EM means
means <- data.frame(emmeans(mod, c("Timepoint", "Hypo60"),
  type = "response",
  pbkrtest.limit = 1e6
))
colnames(means) <- c(
  "Timepoint", "Hypo60", "Mean", "SE", "df", "CI Lower Limit", "CI Upper Limit"
)
# Plot
ggplot(means, aes(
  x = as.numeric(as.character(Timepoint)), y = Mean, colour = Hypo60,
  group = Hypo60
)) +
  geom_point() +
  geom_errorbar(aes(ymin = `CI Lower Limit`, ymax = `CI Upper Limit`),
    width = 3
  ) +
  geom_line() +
  scale_x_continuous(breaks = timepoints) +
  scale_color_manual(values = c("#66C2A5", "#FC8D62")) +
  ylab("EM Mean C-peptide") +
  xlab("Timepoint") +
  theme_bw(base_size = 14) +
  theme(legend.title = element_blank())
```

@@

```{r}
# Fit
mod <- lmer(Glucagon ~ Timepoint * Hypo70 + (1 | study_id / ogtt_num),
  data = glmm_df
)
# EM means
means <- data.frame(emmeans(mod, c("Timepoint", "Hypo70"),
  type = "response",
  pbkrtest.limit = 1e6
))
colnames(means) <- c(
  "Timepoint", "Hypo70", "Mean", "SE", "df", "CI Lower Limit", "CI Upper Limit"
)
# Plot
ggplot(means, aes(
  x = as.numeric(as.character(Timepoint)), y = Mean, colour = Hypo70,
  group = Hypo70
)) +
  geom_point() +
  geom_errorbar(aes(ymin = `CI Lower Limit`, ymax = `CI Upper Limit`),
    width = 3
  ) +
  geom_line() +
  scale_x_continuous(breaks = timepoints) +
  scale_color_manual(values = c("#66C2A5", "#FC8D62")) +
  ylab("EM Mean Glucagon") +
  xlab("Timepoint") +
  theme_bw(base_size = 14) +
  theme(legend.title = element_blank())
```

>>>>

```{r setup}
#| include: false
library(Hmisc)
library(tidyverse)
library(arsenal)
library(pROC)
library(gt)
library(patchwork)
library(lmerTest)
library(emmeans)
library(plotly)
home_dir <- switch(Sys.info()["sysname"],
    "Darwin" = "/Users/tim/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF",
    "Windows" = "C:/Users/Tim/OneDrive - The University of Colorado Denver/Vigers/CF",
    "Linux" = "/home/tim/OneDrive/Vigers/CF"
)
github_dir <- switch(Sys.info()["sysname"],
    "Darwin" = "/Users/tim/Documents/GitHub",
    "Windows" = "C:/Users/Tim/Documents/GitHub",
    "Linux" = "/home/tim/Documents/GitHub"
)
knitr::opts_knit$set(root.dir = home_dir)
```

```{r data cleaning}
# Set seed for bootstrap
set.seed(1017)
# Import data
# See GitHub/CF/Christine Chan/EnVision CF/clean_envision_data.R
load(
    "/Users/tim/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Christine Chan/EnVision CF/Data_Clean/envision_analysis_dataset.RData"
)
```

@@

```{r}
# Limit to those with CGM data (based on mean glucose) and OGTT diagnosis
# Remove CC0083 per Christine (weird CGM)
df <- final_df %>%
    filter(!is.na(mean_sensor), !is.na(Diagnosis), study_id != "CC0083")
# Change specific diagnoses per Christine
df$Diagnosis[df$study_id == "WU0019"] <- c("NGT", "NGT")
df$Diagnosis[df$study_id == "IA0080"] <- "IGT"
# Convert CV units to match Scully et al.
df$cv <- df$cv * 100
# First CGM and OGTT pair only
# df <- df %>%
#     group_by(study_id) %>%
#     slice_min(Date)
```

@@

## Participant Demographics by Diagnosis

```{r results='asis'}
t1 <- tableby(
    Dysglycemia ~
        fe(redcap_data_access_group) +
        kwt(age_visit, "Nmiss", "medianq1q3", "range") +
        kwt(height, "Nmiss", "medianq1q3", "range") +
        kwt(weight, "Nmiss", "medianq1q3", "range") +
        bmi_perc +
        sex +
        fe(origin_race) +
        fe(ethnicity) +
        fe(pancreatic_status) +
        fe(CFTR) +
        corrector_yes_no +
        fev1 +
        fvc +
        a1c_result,
    data = df,
    simulate.p.value = TRUE
)
summary(t1, pfootnote = T)
```

@@

```{r}
r <- roc(CFRD ~ mean_sensor, data = df, quiet = T)
plot(r, print.auc = T, print.thres = T, legacy.axes = T)
ci.auc(r)
gt(coords(r, "best", ret = "all")) %>% fmt_number(decimals = 3)
gt(data.frame(coords(
    r,
    "all",
    ret = c(c(
        "thresh",
        "sensitivity",
        "specificity",
        "fp",
        "tp",
        "fn",
        "tn",
        "npv",
        "ppv"
    ))
))) %>%
    fmt_number(decimals = 3)
```

@@

```{r}
r <- roc(CFRD ~ percent_time_over_140, data = df, quiet = T)
plot(r, print.auc = T, print.thres = T, legacy.axes = T)
ci.auc(r)
gt(coords(r, "best", ret = "all")) %>% fmt_number(decimals = 3)
gt(data.frame(coords(
    r,
    "all",
    ret = c(c(
        "thresh",
        "sensitivity",
        "specificity",
        "fp",
        "tp",
        "fn",
        "tn",
        "npv",
        "ppv"
    ))
))) %>%
    fmt_number(decimals = 3)
```

@@

```{r}
r <- roc(CFRD ~ percent_time_over_180, data = df, quiet = T)
plot(r, print.auc = T, print.thres = T, legacy.axes = T)
ci.auc(r)
gt(coords(r, "best", ret = "all")) %>% fmt_number(decimals = 3)
gt(data.frame(coords(
    r,
    "all",
    ret = c(c(
        "thresh",
        "sensitivity",
        "specificity",
        "fp",
        "tp",
        "fn",
        "tn",
        "npv",
        "ppv"
    ))
))) %>%
    fmt_number(decimals = 3)
```

@@

```{r}
r <- roc(CFRD ~ gmi, data = df, quiet = T)
plot(r, print.auc = T, print.thres = T, legacy.axes = T)
ci.auc(r)
gt(coords(r, "best", ret = "all")) %>% fmt_number(decimals = 3)
gt(data.frame(coords(
    r,
    "all",
    ret = c(c(
        "thresh",
        "sensitivity",
        "specificity",
        "fp",
        "tp",
        "fn",
        "tn",
        "npv",
        "ppv"
    ))
))) %>%
    fmt_number(decimals = 3)
```

@@

```{r}
r <- roc(CFRD ~ standard_deviation, data = df, quiet = T)
plot(r, print.auc = T, print.thres = T, legacy.axes = T)
ci.auc(r)
gt(coords(r, "best", ret = "all")) %>% fmt_number(decimals = 3)
gt(data.frame(coords(
    r,
    "all",
    ret = c(c(
        "thresh",
        "sensitivity",
        "specificity",
        "fp",
        "tp",
        "fn",
        "tn",
        "npv",
        "ppv"
    ))
))) %>%
    fmt_number(decimals = 3)
```

@@

```{r}
r <- roc(CFRD ~ cv, data = df, quiet = T)
plot(r, print.auc = T, print.thres = T, legacy.axes = T)
ci.auc(r)
gt(coords(r, "best", ret = "all")) %>% fmt_number(decimals = 3)
gt(data.frame(coords(
    r,
    "all",
    ret = c(c(
        "thresh",
        "sensitivity",
        "specificity",
        "fp",
        "tp",
        "fn",
        "tn",
        "npv",
        "ppv"
    ))
))) %>%
    fmt_number(decimals = 3)
```

@@

```{r}
r <- roc(CFRD ~ a1c_result, data = df, quiet = T)
plot(r, print.auc = T, print.thres = T, legacy.axes = T)
ci.auc(r)
gt(coords(r, "best", ret = "all")) %>% fmt_number(decimals = 3)
gt(data.frame(coords(
    r,
    "all",
    ret = c(c(
        "thresh",
        "sensitivity",
        "specificity",
        "fp",
        "tp",
        "fn",
        "tn",
        "npv",
        "ppv"
    ))
))) %>%
    fmt_number(decimals = 3)
```

@@

```{r}
#| message: false
#| warning: false
#| fig-height: 12
#| fig-width: 16
# Dotplot
box_p1 <- ggplot(
    df,
    aes(
        x = Dysglycemia,
        y = percent_time_over_140,
        colour = Dysglycemia,
        text = study_id
    )
) +
    geom_jitter() +
    geom_hline(yintercept = 17.5, color = "red") +
    geom_hline(yintercept = 11.3, color = "purple") +
    ggtitle("% Time Over 140 (mg/dL)") +
    theme_bw(base_size = 12) +
    theme(
        legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.x = element_blank(),
        axis.title.y = element_blank()
    ) +
    scale_color_manual(values = c("#4DA8DA", "#80D8C3", "#FFD66B"))
box_p2 <- ggplot(
    df,
    aes(x = Dysglycemia, y = percent_time_over_180, colour = Dysglycemia)
) +
    geom_jitter() +
    geom_hline(yintercept = 3.4, color = "red") +
    geom_hline(yintercept = 3.1, color = "purple") +
    ggtitle("% Time Over 180 (mg/dL)") +
    theme_bw(base_size = 12) +
    theme(
        legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.x = element_blank(),
        axis.title.y = element_blank()
    ) +
    scale_color_manual(values = c("#4DA8DA", "#80D8C3", "#FFD66B"))
box_p3 <- ggplot(
    df,
    aes(x = Dysglycemia, y = mean_sensor, colour = Dysglycemia)
) +
    geom_jitter() +
    geom_hline(yintercept = 112, color = "red") +
    geom_hline(yintercept = 101, color = "purple") +
    ggtitle("Mean glucose (mg/dL)") +
    theme_bw(base_size = 12) +
    theme(
        legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.x = element_blank(),
        axis.title.y = element_blank()
    ) +
    scale_color_manual(values = c("#4DA8DA", "#80D8C3", "#FFD66B"))
box_p4 <- ggplot(
    df,
    aes(x = Dysglycemia, y = cv, colour = Dysglycemia)
) +
    geom_jitter() +
    geom_hline(yintercept = 30.6, color = "red") +
    geom_hline(yintercept = 27.7, color = "purple") +
    ggtitle("Coefficient of Variation (%)") +
    theme_bw(base_size = 12) +
    theme(
        legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.x = element_blank(),
        axis.title.y = element_blank()
    ) +
    scale_color_manual(values = c("#4DA8DA", "#80D8C3", "#FFD66B"))
box_p5 <- ggplot(
    df,
    aes(x = Dysglycemia, y = a1c_result, colour = Dysglycemia)
) +
    geom_jitter() +
    geom_hline(yintercept = 5.8, color = "red") +
    geom_hline(yintercept = 5.75, color = "purple") +
    ggtitle("HbA1c (%)") +
    theme_bw(base_size = 12) +
    theme(
        legend.title = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.x = element_blank(),
        axis.title.y = element_blank()
    ) +
    scale_color_manual(values = c("#4DA8DA", "#80D8C3", "#FFD66B"))
box_p <- box_p1 + box_p2 + box_p4 + box_p3 + box_p5 + plot_layout(ncol = 5)
box_p
ggplotly(box_p1, tooltip = c("text"))
ggplotly(box_p2, tooltip = c("text"))
ggplotly(box_p4, tooltip = c("text"))
ggplotly(box_p3, tooltip = c("text"))
ggplotly(box_p5, tooltip = c("text"))
```

@@

```{r}
# Fit
mod <- lmer(
    Glucose ~ Timepoint * Hypo70 + (1 | study_id / ogtt_num),
    data = glmm_df
)
# EM means
means <- data.frame(emmeans(
    mod,
    c("Timepoint", "Hypo70"),
    type = "response",
    pbkrtest.limit = 1e6
))
colnames(means) <- c(
    "Timepoint",
    "Hypo70",
    "Mean",
    "SE",
    "df",
    "CI Lower Limit",
    "CI Upper Limit"
)
# Plot
ggplot(
    means,
    aes(
        x = as.numeric(as.character(Timepoint)),
        y = Mean,
        colour = Hypo70,
        group = Hypo70
    )
) +
    geom_point() +
    geom_errorbar(
        aes(ymin = `CI Lower Limit`, ymax = `CI Upper Limit`),
        width = 3
    ) +
    geom_line() +
    scale_x_continuous(breaks = timepoints) +
    scale_color_manual(values = c("#66C2A5", "#FC8D62")) +
    ylab("EM Mean Glucose") +
    xlab("Timepoint") +
    theme_bw(base_size = 14) +
    theme(legend.title = element_blank())
```

@@

```{r}
# Fit
mod <- lmer(
    Glucose ~ Timepoint * Hypo60 + (1 | study_id / ogtt_num),
    data = glmm_df
)
# EM means
means <- data.frame(emmeans(
    mod,
    c("Timepoint", "Hypo60"),
    type = "response",
    pbkrtest.limit = 1e6
))
colnames(means) <- c(
    "Timepoint",
    "Hypo60",
    "Mean",
    "SE",
    "df",
    "CI Lower Limit",
    "CI Upper Limit"
)
# Plot
ggplot(
    means,
    aes(
        x = as.numeric(as.character(Timepoint)),
        y = Mean,
        colour = Hypo60,
        group = Hypo60
    )
) +
    geom_point() +
    geom_errorbar(
        aes(ymin = `CI Lower Limit`, ymax = `CI Upper Limit`),
        width = 3
    ) +
    geom_line() +
    scale_x_continuous(breaks = timepoints) +
    scale_color_manual(values = c("#66C2A5", "#FC8D62")) +
    ylab("EM Mean Glucose") +
    xlab("Timepoint") +
    theme_bw(base_size = 14) +
    theme(legend.title = element_blank())
```

@@

```{r}
# Fit
mod <- lmer(
    log(Insulin) ~ Timepoint * Hypo70 + (1 | study_id / ogtt_num),
    data = glmm_df
)
# EM means
means <- data.frame(emmeans(
    mod,
    c("Timepoint", "Hypo70"),
    type = "response",
    pbkrtest.limit = 1e6
))
colnames(means) <- c(
    "Timepoint",
    "Hypo70",
    "Mean",
    "SE",
    "df",
    "CI Lower Limit",
    "CI Upper Limit"
)
# Plot
ggplot(
    means,
    aes(
        x = as.numeric(as.character(Timepoint)),
        y = Mean,
        colour = Hypo70,
        group = Hypo70
    )
) +
    geom_point() +
    geom_errorbar(
        aes(ymin = `CI Lower Limit`, ymax = `CI Upper Limit`),
        width = 3
    ) +
    geom_line() +
    scale_x_continuous(breaks = timepoints) +
    scale_color_manual(values = c("#66C2A5", "#FC8D62")) +
    ylab("EM Mean Insulin") +
    xlab("Timepoint") +
    theme_bw(base_size = 14) +
    theme(legend.title = element_blank())
```

@@

```{r}
# Fit
mod <- lmer(
    log(Insulin) ~ Timepoint * Hypo60 + (1 | study_id / ogtt_num),
    data = glmm_df
)
# EM means
means <- data.frame(emmeans(
    mod,
    c("Timepoint", "Hypo60"),
    type = "response",
    pbkrtest.limit = 1e6
))
colnames(means) <- c(
    "Timepoint",
    "Hypo60",
    "Mean",
    "SE",
    "df",
    "CI Lower Limit",
    "CI Upper Limit"
)
# Plot
ggplot(
    means,
    aes(
        x = as.numeric(as.character(Timepoint)),
        y = Mean,
        colour = Hypo60,
        group = Hypo60
    )
) +
    geom_point() +
    geom_errorbar(
        aes(ymin = `CI Lower Limit`, ymax = `CI Upper Limit`),
        width = 3
    ) +
    geom_line() +
    scale_x_continuous(breaks = timepoints) +
    scale_color_manual(values = c("#66C2A5", "#FC8D62")) +
    ylab("EM Mean Insulin") +
    xlab("Timepoint") +
    theme_bw(base_size = 14) +
    theme(legend.title = element_blank())
```

@@

```{r}
# Fit
mod <- lmer(
    log(C.Peptide) ~ Timepoint * Hypo70 + (1 | study_id / ogtt_num),
    data = glmm_df
)
# EM means
means <- data.frame(emmeans(
    mod,
    c("Timepoint", "Hypo70"),
    type = "response",
    pbkrtest.limit = 1e6
))
colnames(means) <- c(
    "Timepoint",
    "Hypo70",
    "Mean",
    "SE",
    "df",
    "CI Lower Limit",
    "CI Upper Limit"
)
# Plot
ggplot(
    means,
    aes(
        x = as.numeric(as.character(Timepoint)),
        y = Mean,
        colour = Hypo70,
        group = Hypo70
    )
) +
    geom_point() +
    geom_errorbar(
        aes(ymin = `CI Lower Limit`, ymax = `CI Upper Limit`),
        width = 3
    ) +
    geom_line() +
    scale_x_continuous(breaks = timepoints) +
    scale_color_manual(values = c("#66C2A5", "#FC8D62")) +
    ylab("EM Mean C-peptide") +
    xlab("Timepoint") +
    theme_bw(base_size = 14) +
    theme(legend.title = element_blank())
```

@@

```{r}
# Fit
mod <- lmer(
    log(C.Peptide) ~ Timepoint * Hypo60 + (1 | study_id / ogtt_num),
    data = glmm_df
)
# EM means
means <- data.frame(emmeans(
    mod,
    c("Timepoint", "Hypo60"),
    type = "response",
    pbkrtest.limit = 1e6
))
colnames(means) <- c(
    "Timepoint",
    "Hypo60",
    "Mean",
    "SE",
    "df",
    "CI Lower Limit",
    "CI Upper Limit"
)
# Plot
ggplot(
    means,
    aes(
        x = as.numeric(as.character(Timepoint)),
        y = Mean,
        colour = Hypo60,
        group = Hypo60
    )
) +
    geom_point() +
    geom_errorbar(
        aes(ymin = `CI Lower Limit`, ymax = `CI Upper Limit`),
        width = 3
    ) +
    geom_line() +
    scale_x_continuous(breaks = timepoints) +
    scale_color_manual(values = c("#66C2A5", "#FC8D62")) +
    ylab("EM Mean C-peptide") +
    xlab("Timepoint") +
    theme_bw(base_size = 14) +
    theme(legend.title = element_blank())
```

@@

```{r}
# Fit
mod <- lmer(
    Glucagon ~ Timepoint * Hypo70 + (1 | study_id / ogtt_num),
    data = glmm_df
)
# EM means
means <- data.frame(emmeans(
    mod,
    c("Timepoint", "Hypo70"),
    type = "response",
    pbkrtest.limit = 1e6
))
colnames(means) <- c(
    "Timepoint",
    "Hypo70",
    "Mean",
    "SE",
    "df",
    "CI Lower Limit",
    "CI Upper Limit"
)
# Plot
ggplot(
    means,
    aes(
        x = as.numeric(as.character(Timepoint)),
        y = Mean,
        colour = Hypo70,
        group = Hypo70
    )
) +
    geom_point() +
    geom_errorbar(
        aes(ymin = `CI Lower Limit`, ymax = `CI Upper Limit`),
        width = 3
    ) +
    geom_line() +
    scale_x_continuous(breaks = timepoints) +
    scale_color_manual(values = c("#66C2A5", "#FC8D62")) +
    ylab("EM Mean Glucagon") +
    xlab("Timepoint") +
    theme_bw(base_size = 14) +
    theme(legend.title = element_blank())
```
